A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-01 paper/paper.tex
Plotting!
References
Better plottery

\usepackage{ijcai17}
\usepackage{times}

@@

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
\bibliography{paper}

>>>>

\usepackage{ijcai17}
\usepackage{times}
\usepackage{graphicx}

\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
\newcommand{\citep}[1]{\cite{#1}}

@@

\citet{UpcomingAAAIPaper}

\citet{DBLP:conf/cp/McCreeshNPS16}

\citet{DBLP:conf/cp/NdiayeS11}

\section{Computational Experiments}

Dual Xeon E5-2640 v2 CPUs, 64GBytes RAM. Parallel experiments 16 threads (one per hardware core), and 32 with hyper-threading.

\paragraph{No labels, undirected}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-cumulative.pdf}
    \caption{MCS Plain instances, cumulative runtimes}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-cumulative.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, cumulative runtimes}
\end{figure}

\paragraph{Vertex and edge labels, directed}

\paragraph{No labels, undirected, connected}

\paragraph{Vertex and edge labels, connected}

\paragraph{Large subgraph isomorphism instances}

\paragraph{Compared to CP FC}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Runtimes}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs CP-FC, Runtimes}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS Plain instances, James vs CP-FC, Nodes}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs CP-FC, Nodes}
\end{figure}

\bibliographystyle{named}
\bibliography{paper}
